---
title: "A simple pipeline"
author: "Mike Smith"
date: "January 6th, 2019"
output: html_document
---

# Installing the required packages

We install a package crucial to the workflow.  

<!-- We don't run it every time as its already installed on my computer -->

```{r, installation, eval = FALSE, echo = TRUE}
install.packages('ggplot2')
```

# Data creation

Imagine this step takes a really long time.  We want to include the code for completeness, but we don't want to re-run it every time we generate the document.  We then load a saved version of the data but hide that code in the final output.

```{r, create-cats, eval = FALSE}
cats <- data.frame(coat = c("calico", "black", "tabby"), 
                    weight = c(2.1, 5.0,3.2), 
                    likes_string = c(TRUE, FALSE, TRUE))
write.csv(x = cats, file = "feline-data.csv", row.names = FALSE)
```

```{r, load-cats, include = FALSE}
cats <- read.csv(file = "feline-data.csv")
```

# Creating a convicing plot

We look at the relationship between cat weight and their liking of string

```{r, plotting}
library(ggplot2)
ggplot(cats, aes(x = likes_string, y = weight, 
                 group = likes_string,
                 fill = likes_string)) + 
    geom_boxplot()
```

It appears disliking of string indicates a fat cat!

# Current R session

```{r}
sessionInfo()
```